---
title: "BiVariate - Categorical and Categorical"
output: html_notebook
author: "Ashish Khandelwal"
---
#################################################################################################
Important Note - The results you see in the video and in this notebook may diverge slightly due to differences in the datasets (we provide small dataset to you).
##################################################################################################

```{r}
#install.packages("ggplot2")
#install.packages("dplyr")
library(dplyr)
library(ggplot2)
library(stringr)
```

Read the data as df
```{r}
df <- read.csv("ities_prem.csv")
```

Create data with Count for each Department and Weekday Combination

```{r}
cross_tab <- xtabs(~Department +WeekDay, data=df)
department <- rownames(cross_tab)
weekday <- colnames(cross_tab)

df1 <- expand.grid(department,weekday)
Count <- as.vector(cross_tab)
df1$Count <- Count
```


Check what's in the df1
```{r}
df1
```

Var1 is Department and Var2 is the weekday. Count shows the count for department and day combination. 

The number of Observations for each Department for Each day of the week
```{r, fig.height=6, fig.width=6}
p1 <- ggplot(data = df1, aes(x= Var1, y = factor(Var2), size = Count))

p2 <- p1 + geom_point(col = "red") + labs(x = "Department", y="Weekday") # since our variables are read as var1 and var2, we need to provide labels using the "labs" function.

p2

```

One very easy way to create the graph above is using the following code. This uses a simple and elegant geom_object "geom_count". 

However, the one shown above takes you through the details of xtables, which you may also use to assess the relationship by observing numbers in the df1. 
```{r, fig.height=6, fig.width=6}
p1 <- ggplot(data = df, aes(x= Department, y = factor(WeekDay)))

p2 <- p1 + geom_count(color = "red")
p2
```







