---
title: "Introduction to ggplot2 syntax"
output: html_notebook
author: "Ashish Khandelwal"
---
#################################################################################################
Important Note - The results you see in the video and in this notebook may diverge slightly due to differences in the datasets (we provide small dataset to you).
##################################################################################################

```{r}
#install.packages("ggplot2")
#install.packages("dplyr")
library(dplyr)
library(ggplot2)
library(stringr)
```

Read the data as df
```{r}
df <- read.csv("C:/Users/ashis/OneDrive/Data/ities_prem.csv")
```


1) First component of ggplot - Data 

We specify the dataframe name in the ggplot function and save the object created in "p"
```{r fig.height= 6, fig.width=12}
p <- ggplot(data = df)

p
```

2) Second component of ggplot - Aesthetics Mapping --> mapping = aes()


```{r, fig.height= 6, fig.width=12}
p1 <- ggplot(data = df, mapping = aes(x = Price))

p1
```


3) Third component of ggplot - Geometric Object - For example, Histogram, Boxplot, Scatter Plot

```{r, fig.height= 6, fig.width=12}

p2 <- p1 + geom_histogram(bins = 200) # The object p1 is the one created above

# We could have used the following command also

p2 <- ggplot(data = df, mapping = aes(x = Price)) + geom_histogram(bins = 200)

p2
```


