---
title: "Univariate Exploration for Numeric Variables"
output: html_notebook
author: "Ashish Khandelwal"
---
#################################################################################################
Important Note - The results you see in the video and in this notebook may diverge slightly due to differences in the datasets (we provide small dataset to you).
##################################################################################################

```{r}
#install.packages("ggplot2")
#install.packages("dplyr")
library(dplyr)
library(ggplot2)
library(stringr)
```

Read the data as df
```{r}
df <- read.csv("ities_prem.csv")
```



Histogram for Price 
```{r, fig.height= 6, fig.width=12}
p1 <- ggplot(data = df, mapping = aes(x = Price))

p1 + geom_histogram(bins = 200) # play with this argument "bins"
```



Histogram for Price  - Zooming in on a narrow range of Y to get a better view
```{r, fig.height= 6, fig.width=12}
p2 <- p1 + geom_histogram(bins = 200) + coord_cartesian(ylim = c(0,50))
p2
```




Histogram for Price - Log transforming our data to see if better picture emerges 
```{r, fig.height= 10, fig.width=12}
p1_log <- ggplot(data = df, mapping = aes(x = log(Price)))

p2_log <- p1_log + geom_histogram(bins = 30) # play with this argument 
p2_log
```




Density instead of Count
```{r, fig.height= 6, fig.width=12}
p2_log <- p1_log + geom_histogram(aes(y = ..density..), bins=50) # density shows proprotions instead of count

p2_log 
```



Boxplot for Price

```{r, fig.height= 6, fig.width=12}
p1 <-  ggplot(data = df, mapping = aes(y = Price))

p2 <- p1 + geom_boxplot()

p2
```


We see many outliers. There are very high value of prices. May be these are catering orders. 


Zoom into a smaller range for Price (0-50) to see if we can see the boxplot. 
```{r, fig.height= 6, fig.width=12}
p1 <-  ggplot(data = df, mapping = aes(y = Price))

p2 <- p1 + geom_boxplot() + coord_cartesian(ylim = c(0,50))

p2
```


Still many outliers. 



Boxplot on log(Price) 
```{r, fig.height= 6, fig.width=12}
p1_log <-  ggplot(data = df, mapping = aes(y = log(Price)))

p2_log <- p1_log + geom_boxplot()

p2_log
```


Due to log transformation, there are a few outliers on the lower side also. 










































