---
title: "Univariate Exploration for a Categorical Variable"
output: html_notebook
author: "Ashish Khandelwal"
---

#################################################################################################
Important Note - The results you see in the video and in this notebook may diverge slightly due to differences in the datasets (we provide small dataset to you).
##################################################################################################


```{r}
#install.packages("ggplot2")
#install.packages("dplyr")
library(dplyr)
library(ggplot2)
library(stringr)
```


In this lesson we will see how to visually epxlore a Categorical Variable. 

In a categorical variable, you visualize either their frequencies or proportions. 

For exploring catgeorical variable, we create bar charts 


Read the data as df
```{r}
df <- read.csv("ities_prem.csv")
```


```{r fig.width = 15, fig.height = 8}
p1 <- ggplot(data = df %>% filter(Premium ==1), mapping = aes(x= LineItem)) + geom_bar()

p1
```

We see that the most dominant Lineitem (with almost 50% proportion) among the one with very high prices are Catering. This makes sense. 

Next, dominant ones are "Salmon and Wheat Bran Salad" and "Grow-Your-Own-Mushroom-Kits"



If we want to flip the coordinates, we can chnage another component "coordinate"'s default setting to "flip"

```{r fig.width = 15, fig.height = 8}
p1 <- ggplot(data = df %>% filter(Premium ==1), mapping = aes(x= LineItem)) + geom_bar(stat =)

p1 + coord_flip()
```



Showing percentages instead of count - using "y = ..count../ sum(..count..)"

Note the "aes" in the "geom_bar" is for managing the what goes on the y-axis
```{r fig.width = 15, fig.height = 8}
p1 <- ggplot(data = df %>% filter(Premium ==1), mapping = aes(x= LineItem, y = Price)) + 
       geom_bar(aes(y=..count../sum(..count..))) +
        scale_y_continuous(labels = scales::percent_format())

p1 
```


Percentage chart with coordinates flipped

```{r fig.width = 15, fig.height = 8}
p1 <- ggplot(data = df %>% filter(Premium ==1), mapping = aes(x= LineItem, y = Price)) + 
       geom_bar(aes(y=..count../sum(..count..))) +
        scale_y_continuous(labels = scales::percent_format())

p1 + coord_flip()

```



