---
title: "Dplyr Filter and Select Notebook"
output: html_notebook
author: "Ashish Khandelwal"
---
#####################################################################################################
## Important Note - The results you see in the video and in this notebook may diverge slightly due to 
## differences in the datasets (we provide small dataset to you).
#####################################################################################################


This is an R Notebook and not an R script. Here, we need not use "#" to make comments. However, to differentiate between comments and code we use back ticks ``` before and after the code. 

As you can see below, comments are typed without "#". Code is written in what is called a code chunk.

Code chunk is created and ended by ```. Thus, anything typed between two sets of backticks is cosndiered a code in R Notebook. 


Lesson Goals- 

In this lesson we will discuss two functions:

1) Filter  - for filtering rows 

2) Select - for selecting columns 

```{r}
install.packages("dplyr")
library("dplyr")
```


In the command below, we read the dataset as "df" 
```{r}
df <- read.csv("ities.csv", stringsAsFactors = FALSE)  # make sure the data "ities.csv" is in your working directory
```

Filter 
Filter function takes two arguments: 
i) dataframe
ii) column with the condition 


1. Select all the rows where cost > 11

```{r}
df_cost_greater_11 <- filter(df, Cost > 11)
```


Multiple Conditions 

2. Select all the rows where cost > 11 and Price < 15
```{r}
df_cost_11_price_13 <- filter(df, Cost > 11 & Price > 13)
```


3. Select all the rows where cost > 11 OR Price < 15
```{r}
df_cost_11_price_13 <- filter(df, Cost >11 | Price>13)
```


Select
Select function takes two arguments: 
i) dataframe
ii) column name(s). If multiple columns they need to be separated by a ",".  

1. Select the column Cost
```{r}
df_cost <- select(df, Cost)
```


2. Select both Cost and Price
```{r}
df_Cost_Price <- select(df, Cost, Price) 
```







