---
title: "Feature Creation Using Mutate Function"
output: html_notebook
author: "Ashish Khandelwal"
---

#####################################################################################################
## Important Note - The results you see in the video and in this notebook may diverge slightly due to 
## differences in the datasets (we provide small dataset to you).
#####################################################################################################


Mutate - from dplyr package 

Load the package. Fisrt install, if not installed already
```{r}
library(dplyr)
```

Read the data as df
```{r}
df  <- read.csv("ities.csv")
```

Mutate function to create a new column


You specify two things for each column you want to create: name of the new column and the way to create the column

In the column below, we create a variable "premium" on the basis of price being higher than mean + 2 std dev
We use the ifelse function to create the new column named "Premium". Ifelse works the same way it works in Excel. 
```{r}
df <- df %>% mutate(Premium = ifelse(Price > (mean(Price, na.rm=TRUE)+ 2*sd(Price, na.rm=TRUE)),1,0))
```

In "(mean(Price, na.rm=TRUE)+ 2*sd(Price, na.rm=TRUE)", we use "na.rm =TRUE" to ask R to ignore if there are missing values. Mean, sum, etc. won't work without this "na.rm=TRUE" if there are missing values.  

We can check the LineItems in the premium category now. 

Below, we filter the rows where premium is 1 and then select the column LineItem.  Using distinct function allows us to get the unique names of the LineItems 
```{r}
premium_items <- df %>% filter(Premium == 1) %>% select(LineItem) %>% distinct()

premium_items
```

